\documentclass{article}
                            
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage{url}
\usepackage[margin=0in]{geometry}
\usepackage{adjustbox}
\usepackage{xparse}% http://ctan.org/pkg/xparse
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{tikz}
\usepackage{fontawesome}
\usetikzlibrary{shapes}
%
\definecolor{myDarkGray}{RGB}{42,47,66}
\definecolor{myOffWhite}{RGB}{240,240,240}
\definecolor{myLightGray}{RGB}{200,200,200}
\definecolor{myWhite}{RGB}{255,255,255}
%
\NewDocumentCommand{\myrule}{O{1pt} O{3pt} O{black}}{%
  \par\nobreak % don't break a page here
  \kern\the\prevdepth % don't take into account the depth of the preceding line
  \kern#2 % space before the rule
  {\color{#3}\hrule height #1 width\hsize} % the rule
  \kern#2 % space after the rule
  \nointerlineskip % no additional space after the rule
}
%
\NewDocumentCommand{\mydoublerule}{O{1pt} O{3pt} O{black}}{%
  \par\nobreak % don't break a page here
  \kern\the\prevdepth % don't take into account the depth of the preceding line
  \kern#2 % space before the rule
  {\color{#3}\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt } % the rule
  \kern#2 % space after the rule
  \nointerlineskip % no additional space after the rule
}
%
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
%
\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers
%
\newcommand{\MyName}[2]{
	\noindent
	\colorbox{myDarkGray}{
		\parbox{8.5in}{
		\vbox to 1in {
			\vfil
			\begin{minipage}[t]{0.8\textwidth}
			\textcolor{white}{
				\textbf{\Huge #1}\\
				\vspace{5pt}\\
				\textbf{\Large #2}
			}
			\end{minipage}
			\vfil
		}
		}
		\par
	}
}
%
\newcommand{\getelement}[2]{% \getelement{<array>}{<num>}
  \@ifundefined{#1@0}% <array> not defined
    {\@latex@error{Array #1 undefined}\@ehc}{}
  \expandafter\ifnum\csname #1@0\endcsname<#2 % <num> out of range
    \@latex@error{Array #1 only has \csname #1@0\endcsname\space elements}\@ehc
  \fi
  \csname #1@#2\endcsname% Print element
}
%
\newcommand{\filledmarker}{\raisebox{0.5pt}{\tikz{\node[draw,scale=0.6,circle,fill=black](){};}}}
\newcommand{\unfilledmarker}{\raisebox{0.5pt}{\tikz{\node[draw,scale=0.6,circle,fill=none](){};}}}
%
\newcommand{\beginnerscale}{
	\filledmarker\hspace{.1mm}
	\unfilledmarker\hspace{.1mm}
	\unfilledmarker\hspace{.1mm}
	\unfilledmarker\hspace{.1mm}
	\unfilledmarker
}
\newcommand{\beginnerprofscale}{
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\unfilledmarker\hspace{.1mm}
	\unfilledmarker\hspace{.1mm}
	\unfilledmarker
}
\newcommand{\proficientscale}{
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\unfilledmarker\hspace{.1mm}
	\unfilledmarker
}
\newcommand{\profexpertscale}{
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\unfilledmarker
}
\newcommand{\expertscale}{
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\filledmarker\hspace{.1mm}
	\filledmarker
}
%
\newcommand{\MyNarrative}[1]{
	\begin{changemargin}{.1in}{.1in}
	#1
	\end{changemargin}
	\mydoublerule
}
%
\newcommand{\PersonalData}[4]{
	\textbf{Contact Information}
	\myrule[1pt][5pt]
	#1\\
	#2\\
	\\[1pt]
	\faPhone \quad #3\\
	\faEnvelope \quad #4\\
	\faLinkedin \quad /in/justinrfox\\
	\\[6pt]
}
%
\newcommand{\KeySkills}[5]{
	\textbf{Key Skills}
	\myrule[1pt][5pt]
	\small #1\\
	\small #2\\
	\small #3\\
	\small #4\\
	\small #5\\
	\\[6pt]
}
%
\newcommand{\Platforms}[6]{
	\textbf{Targeted Platforms}
	\myrule[1pt][5pt]
	\begin{tabular}{ l r }
	\small #1 &
	\small #2\\
	\small #3 &
	\small #4\\
	\small #5 &
	\small #6\\
	\end{tabular}
	\\[6pt]
}
%
\newcommand{\Languages}[1]{
	\textbf{Languages}
	\myrule[1pt][5pt]
	\begin{tabular}{ l r }
	\small C\# &
	\small \expertscale\\
	\small C++ &
	\small \profexpertscale\\
	\small Dart/Flutter &
	\small \proficientscale\\
	\small SQL &
	\small \beginnerprofscale\\
	\small Javascript &
	\small \beginnerprofscale\\
	\small Python &
	\small \beginnerprofscale\\
	\small Matlab &
	\small \beginnerprofscale\\
	\small Rust &
	\small \beginnerscale\\
	\end{tabular}
	\\[6pt]
}
%
\newcommand{\DeveloperTools}[8]{
	\textbf{Development Tools}
	\myrule[1pt][5pt]
	\begin{tabular}{ l r }
	\small #1 &
	\small #2\\
	\small #3 &
	\small #4\\
	\small #5 &
	\small #6\\
	\small #7 &
	\small #8\\
	\end{tabular}
	\\[6pt]
}
%
\newcommand{\Certifications}[1]{
	\textbf{Certifications}
	\myrule[1pt][5pt]
	\small #1\\
	\\[6pt]
}
%
\newcommand{\Interests}[3]{
	\textbf{Research Interests}
	\myrule[1pt][5pt]
	\small #1\\
	\small #2\\
	\small #3\\
	\\[6pt]
}
%
\newcommand{\EducationHeader}[1]{
	\begin{changemargin}{.1in}{.1in}
	\textbf{\Large Education}
	\myrule[1pt][5pt]
	\end{changemargin}
}
%
\newcommand{\SchoolEntry}[3]{
	\begin{changemargin}{.1in}{.1in}
		\begin{minipage}[t]{1in}
		\textbf{#1}
		\end{minipage}
		\begin{minipage}[t]{5in}			
			\begin{flushleft}
				\textbf{#2}\\
				\textit{\textbf{#3}}
			\end{flushleft}
		\end{minipage}
	\end{changemargin}
	\vspace{1pt}
}
%
\newcommand{\References}{
	\textbf{References}
	\myrule[1pt][5pt]
	Available upon request.
}
%
\newcommand{\Education}{
	\textbf{Education}
	\myrule[1pt][5pt]
	\textit{\textbf{Georgia Institute of Technology}}\\
	\hspace*{-3mm}
	\begin{tabular}{ l r }
		\small MS Electrical Engineering &
		\small 08/06\\
		\small BS Electrical Engineering &
		\small 12/03\\
	\end{tabular}
	\\[6pt]
}
%
\newcommand{\ExperienceHeader}{
	\begin{changemargin}{.1in}{.1in}
	\textbf{\Large Experience}
	\myrule[1pt][5pt]
	\end{changemargin}
}
%
\newcommand{\ExperienceEntry}[5]{
		\begin{minipage}[t]{1in}
			\begin{flushleft}
				\textbf{#1}
			\end{flushleft}
		\end{minipage}
		\begin{minipage}[t]{5in}	
			\begin{flushleft}
				\textbf{#2}\\
				\textit{\textbf{#3}}\\
				\noindent \justifying{#4}\\[4pt]
				\small #5
			\end{flushleft}
		\end{minipage}
\\[6pt]
}
%
\newcommand{\ExperienceEntryFullWidth}[5]{
	\begin{minipage}[t]{1in}
		\begin{flushleft}
			\textbf{#1}
		\end{flushleft}
	\end{minipage}
	\begin{minipage}[t]{0.86\linewidth}	
		\begin{flushleft}
			\textbf{#2}\\
			\textit{\textbf{#3}}\\
			\noindent \justifying{#4}\\[4pt]
			\small #5
		\end{flushleft}
	\end{minipage}
\\[6pt]
}
%
\begin{document}%
\MyName{Justin Fox}{Project Manager / Team Leader / Software Engineer}
\begin{minipage}[t]{0.73\linewidth}
	\colorbox{myWhite}{
		\vbox to 9.8in{
			\MyNarrative{An experienced engineer with a diverse background spanning software development, 
			system engineering, project management and functional team management. Software development 
			skills cover a wide range of modern platforms and a variety of different software development 
			environments. Management experience includes 8 years serving as a Branch Head, charged with directing 
			a team of software developers and curating a wide portfolio of applications across different deployment 
			environments. Functioned as a level 1 Project Director over multiple customer funded programs with 
			individual budgets in excess of \$1M and a proven track record of finishing on time and on budget.}
			\ExperienceHeader
			\ExperienceEntry{Mar 2023 - Present}
			{Branch Head / Senior Research Engineer}
			{Georgia Tech Research Institute}
			{Functional leader of a team of 10 engineers managing a portfolio of software products across a variety of
			of development and deployment environments. Our team and portfolio span a wide breadth of skillsets ranging 
			from time-critical applications running hyper-parellellized pipelines to human centric user interfaces
			developed for both desktop and web environments. Established an agile culture within the team facilitating
			periodic planning meetings, daily scrums and retrospectives. Authored and oversaw the employment of our 
			development and deployment pipelines that enable our continuous integration and testing across all work products. 
			Successfully managed multiple programs with budgets in excess of \$1M from inception through final delivery. 
			Nurtured multiple customer relationships that have resulted in many awards in excess of \$1M. }
			{--Project Management --Team Leadership --Software Architect --Program Development}
			\ExperienceEntry{Jun 2018 - Mar 2023}
			{Senior Research Engineer}
			{Georgia Tech Research Institute}
			{Lead software engineer on a large radar development program responsible for design, development, test 
			and integration of the software components that monitor and control the collection of high power equipment 
			critical to a functional radar. Developed and implemented a configuration management strategy capable of 
			tracing changes from requirement derivation through implementation and ultimately continuous delivery. 
			Project director on multiple programs. Primary author of a Software Development Kit aiming to enable the 
			development of a library of interchangeable Radar algorithms supporting the expansion to a software 
			reconfigurable radar system. }
			{--Windows Application Development --Configuration Management --Project Management}
			\ExperienceEntry{Jun 2016 - Present}
			{Consultant}
			{Deep Fried Software}
			{Sole software developer responsible for creating and maintaining a web service facilitating parent 
			teacher communication at local preschools. The service included a web portal as well as Android and 
			iOS applications. This project was active for over a year but has since been retired due to the rise 
			of free alternatives.}
			{--Full Stack Web Development	--Android Development --iOS Development --Python Development}
			\ExperienceEntry{Jun 2012 - Jun 2018}
			{Branch Head / Senior Research Engineer}
			{Georgia Tech Research Institute}
			{Responsible for leading a team of 8-12 software developers primarily focused on developing Microsoft 
			Windows based desktop applications. Managed the branch staffing needs starting with backlog projections, 
			then talent scounting through the final hiring decision. Functioned as lead developer across many of the 
			projects, helping to establish requirements, define an architecture, then shape and implement the design. 
			Established an agile culture requiring daily communication within the team as well as continuous 
			integration and delivery. Managed multiple programs as a level 1 project director.}
			{--Windows Application Development --Team Management --Project Management}
			\vfill
		}
	}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.25\linewidth}
	\colorbox{myLightGray}{
	\vbox to 9.8in{
			\PersonalData{58 Northcutt St.}{Marietta, GA 30064}{404.903.1269}{justinrfox@hotmail.com}
			\KeySkills{Software Development}{Program Management}{Team Management}{System Engineering}{Development/Operations (DevOps)}
			\Platforms{Windows Desktop}{iOS}{Windows Mobile}{Android}{Postgres}{Linux}
			\DeveloperTools{Git}{Atlassian Suite}{Visual Studio}{Android Studio}{Jenkins}{Google Cloud}{Docker}{Virtualbox}
			\Languages{}
			\Interests{Radar Design}{High Performance Computing}{Developer Productivity}
			\Certifications{Certified Scrum Master}
			\Education
			\References
			\vfill
		}
	}
\end{minipage}%
\newpage
\noindent
\begin{minipage}[t]{0.99\linewidth}
	\colorbox{myWhite}{
	\vbox to 9.8in{
		\ExperienceEntryFullWidth{Jun 2007 - Jun 2012}{Research Engineer II}{Georgia Tech Research Institute}{Program Manager of the Tactical Aircraft Defensive Suite (TADS) Program which consisted of a continually evolving portfolio of studies intended to improve integration among the individual systems comprising the Electronic Warfare suite on-board a set of legacy air platforms. Responsibilities included general program oversight, customer communication and personal participation in a number of the studies. Studies spanned the gamut from hardware-in-the-loop lab testing, range testing, software development and theoretical studies. Hosted a bi-annual TADS conference with an audience comprised of 40+ attendees from Government and Industry.}{--System Engineering --Team Management --Project Management }
		\ExperienceEntryFullWidth{Dec 2004 - Jun 2007}{Research Engineer I}{Georgia Tech Research Institute}{Assisted in the development of multiple Microsoft Windows based desktop applications designed to support hardware-in-the-loop testing and Mission Data support tools for an EW integration subsystem onboard legacy airborne tactical platforms. Provided general System Engineering support for multiple OFP releases for the same EW integration subsystem. Functioned as a level 1 project director over a program culminating in a major release of the subsystem OFP.}{--Windows Application Development --System Engineering --Project Management}
		\vfill
	}
	}
\end{minipage}%
\end{document}%
